\documentclass[letter,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}

% Traditional Serif Font
\usepackage{fontspec}
\setmainfont{Spectral-Regular}[
    Path = ./fonts/,
    Extension = .ttf,
    BoldFont = Spectral-Bold,
    ItalicFont = Spectral-Italic,
    BoldItalicFont = Spectral-BoldItalic
]

\definecolor{primary}{RGB}{0, 0, 0}
\hypersetup{colorlinks=true, urlcolor=blue}

% Section Formatting
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1em}{0.5em}

\newcommand{\role}[4]{
    \noindent\textbf{#1} \hfill #3 \\
    \textit{#2} \hfill #4 \\
}

\begin{document}

\begin{center}
    {\huge \textbf{Takasur Azeem}} \\
    Louisville, KY | (502) 442-8429 | \href{mailto:takasurazeem@gmail.com}{takasurazeem@gmail.com} \\
    \href{https://linkedin.com/in/takasur-azeem}{LinkedIn: takasur-azeem} | \href{https://github.com/takasurazeem}{GitHub: takasurazeem}
\end{center}

\section*{Summary}
Performance-driven Software Engineer with extensive experience in the iOS ecosystem, specialized in architecting high-scale applications for 400M+ users. Expertise in Server-Driven UI (SDUI), real-time systems, and AI-assisted development infrastructure. Proven track record of delivering 90+ production features while optimizing developer velocity and system reliability in enterprise environments.

\section*{Technical Skills}
\noindent\textbf{Languages:} Swift 6, SwiftUI, UIKit, Objective-C, Bash, JSON, XML, SQL \\
\textbf{Platforms:} iOS, iPadOS, watchOS, macOS, Apple TV, Firebase \\
\textbf{AI \& Automation:} AI Agent Orchestration, MCP (Model Context Protocol), Claude Code, Roo Code, Prompt Engineering, GitHub Copilot \\
\textbf{Tools \& Utilities:} Xcode 26, Git, Proxyman, Fastlane, SonarQube, Jira, CocoaPods, Carthage, SPM \\
\textbf{Architecture:} MVVM, TCA (The Composable Architecture), SDUI, Modular Architecture, REST APIs \\
\textbf{Database:} Core Data, Realm, SQLite, FireStore, RDS \\
\textbf{Methodology:} Agile, Scrum, TDD (Test Driven Development), CI/CD (Travis, Jenkins)

\section*{Selected Accomplishments}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Shipped 93+ production PRs (50K+ LOC) for The Weather Channel app, maintaining 99.9\% crash-free sessions.
    \item Architected an enterprise-scale Real-Time Rain Live Activities system serving millions of users.
    \item Engineered an AI-driven dev-tooling stack that reduced context overhead by 65\% and increased velocity by 25\%.
    \item Led the end-to-end development of a 31K+ LOC watchOS companion app from POC to production-ready.
\end{itemize}

\section*{Professional Experience}

\role{The Weather Channel}{Software Engineer}{August 2022 -- Present}{Atlanta, GA (Remote)}
\noindent\textbf{Project Summary:} Architecting and scaling the world's most accurate forecaster app (416M active users) with a focus on real-time data visualization, Live Activities, and server-driven onboarding experiences.

\noindent\textbf{Responsibilities:}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Architected Real-Time Rain Live Activities system using ActivityKit and push-to-start token lifecycles, integrating with UPSX alerts service for server-side token synchronization.
    \item Engineered a complete watchOS companion app (31K+ LOC) featuring multi-tab navigation, interactive precipitation charts, and offline caching systems for weather data.
    \item Developed and optimized 4 major components in the Customer Onboarding flow using Server-Driven UI (SDUI) to streamline premium conversions and registration value propositions.
    \item Created iMessages Current Observations Card with view\_data API integration, enhancing cross-platform sharing capabilities.
    \item Implemented deep linking to the TWC app via URL schemes, improving user re-engagement from external notifications.
    \item Integrated Swift 6 concurrency patterns (Actors, Sendable) and optimized thread safety using OSAllocatedUnfairLock to reduce crash rates by 35\%.
    \item Enhanced user experience with sophisticated Haptic Feedback systems integrated into the radar timeline and hourly forecast list views.
    \item Optimized app loading time by 40\% through strategic I/O management and resolving main-thread performance bottlenecks.
    \item Designed AI agent infrastructure with 7 specialized skills (Git automation, PR creation, Figma-to-Code) reducing context overhead by 65\%.
    \item Modernized the development environment by refactoring the Xcode project to use buildable folders instead of groups, improving filesystem sync.
    \item Managed App Store submission and approval processes for major releases, coordinating with cross-functional teams of 12+ members.
    \item Standardized technical documentation with 600+ line architecture guides and Mermaid system diagrams for team DX.
\end{itemize}
\noindent\textbf{Tools Utilized:} Swift 6, SwiftUI, Xcode 26, ActivityKit, SDUI, Core Data, Proxyman, Claude Code, Fastlane, Firebase, Pangea Logging, Haptics SDK.

\role{MTBC / CareCloud}{Software Engineer}{July 2021 -- August 2022}{Rawalpindi, PK}
\noindent\textbf{Project Summary:} Promoted from iOS Developer to Software Engineer to lead architectural modernization and systems integration for a top-tier US telehealth platform serving 40,000+ providers.

\noindent\textbf{Responsibilities:}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Architected and developed a complex integration solution to consolidate two disparate backend systems, ensuring a unified user experience across the telehealth suite.
    \item Engineered a custom authentication module enabling seamless SSO-style migration for legacy application users into the modernized iOS platform.
    \item Championed the adoption of Test-Driven Development (TDD) methodologies, significantly increasing code coverage and reducing regression defects.
    \item Established and configured SonarQube for automated code analysis, identifying and remediating critical security and performance issues.
    \item Automated the build and deployment pipeline using Fastlane, streamlining app distribution to QA teams and reducing release cycles.
    \item Simplified the incorporation of new insurance-mandated compliance changes, reducing implementation time for regulatory features by 15\%.
    \item Conducted in-depth technical interviews and behavioral assessments for iOS engineering hires, maintaining a 90\% retention rate.
    \item Mentored junior developers on MVVM architecture and modular code design, resulting in a 30\% improvement in team velocity.
\end{itemize}
\noindent\textbf{Tools Utilized:} Swift, SwiftUI, Objective-C, UIKit, Composable Architecture (TCA), Fastlane, SonarQube, CoreData, RESTful APIs, TDD, Travis-CI, Microsoft AppCenter.

\role{Freelance / Multiple Clients}{Software Developer}{June 2018 -- July 2021}{Remote}
\noindent\textbf{Project Summary:} End-to-end development of custom mobile and web solutions for international clients across diverse industries.

\noindent\textbf{Responsibilities:}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Delivered 50+ successful projects with 100\% client satisfaction rate across Upwork and Fiverr.
    \item Developed automated solutions that scaled user bases from hundreds to 10,000+ active users.
    \item Managed full project lifecycles: requirement gathering, UI/UX design, development, and deployment.
\end{itemize}
\noindent\textbf{Tools Utilized:} Swift, SwiftUI, Firebase, JavaScript, Automated Scripts.

\role{SemangiX}{Software Engineer}{September 2018 -- September 2019}{Gujranwala, PK}
\noindent\textbf{Responsibilities:}
\begin{itemize}[noitemsep, topsep=2pt]
    \item Headed two high-impact projects resulting in a 30\% boost in annual company revenue.
    \item Optimized RESTful API data retrieval times by 20\% through caching and database query refinement.
    \item Coordinated team skill development, increasing proficiency in new technologies and methodologies by 40\%.
\end{itemize}
\noindent\textbf{Tools Utilized:} iOS SDK, REST APIs, SQL, MVC, Git.

\section*{Education}
\noindent\textbf{MS in Software Engineering (Coursework Completed)} \hfill 2019 -- 2021 \\
International Islamic University Islamabad (IIUI) \\

\noindent\textbf{BS in Information Technology} \hfill 2013 -- 2017 \\
University of Sargodha

\section*{Certifications}
\noindent\textbf{iOS Development:} Test-Driven Development, Architecture, Protocol-Oriented Programming, Async/Await \& Actors (Udemy), ARKit Course. \\
\textbf{Git:} Branches, Merges, and Remotes.

\end{document}
