\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% weather.com
%====================
\subsection{{Software Engineer iOS / \href{https://weather.com/}{TheWeatherChannel (IBM)} \hfill August 2022 - Present}}
\subtext{\href{https://weather.com/}{IBM/TheWeatherChannel} \hfill Atlanta, GA}
\begin{zitemize}
\item[] Joined the weather company, an IBM business, to work on The Weather Channel app, which is the World's Most Accurate Forecaster with over 300 thousand monthly app installs on iOS alone.
\item[] Key achievements:

\item Spearheaded the development and enhancement of key features in the TWC iOS app, resulting in a significant 35\% reduction in crash rates and a 25\% increase in user engagement.

\item Proactively identified and addressed bottlenecks, leading to an impressive 40\% improvement in the app's average loading time and a smoother user experience. This initiative contributed to a 20\% rise in user ratings and a 15\% boost in positive reviews on the App Store.

\item Improved the location search component module, enhancing efficiency by 50\% while implementing five fail-safe mechanisms to reduce errors.
\end{zitemize}

%====================
% CareCloud
%====================
\subsection{{iOS Developer / \href{https://www.carecloud.com/breeze/}{BREEZE PRACTICE} \hfill July 2021 - August 2022}}
\subtext{\href{http://www.carecloud.com}{CareCloud} \hfill Rawalpindi, Punjab}
\begin{zitemize}
\item[] Joined the US top telehealth company with 40k+ Providers, 70+ Medical Specialties, and Serving in 50 States
\item Implemented industry-leading software design patterns and architectures, resulting in a 20\% increase in application performance.
\item Streamlined the incorporation of new changes mandated by insurance and clients, ensuring compliance and reducing implementation time by 15\%.
\item Distinguished as a behavioral and technical interviewer for iOS candidates, playing a pivotal role in recruiting top talent, with a 90\% hiring success rate.
\item Mentored and guided interns and Junior iOS Developers, assisting the team in task completion and providing expert guidance, resulting in a 30\% improvement in team's productivity.

\end{zitemize}

%====================
% nullBrainer
%====================
\subsection{{iOS Developer / \href{https://sureti.com/}{Sureti} \hfill May 2021 - June 2021}}
\subtext{\href{http://www.nullbrainer.io}{nullBrainer} \hfill Lahore, Punjab}
\begin{zitemize}
\item Spearheaded iOS development as the lead developer, collaborating seamlessly with cross-functional teams (Web, Android, and Backend), resulting in a 30\% reduction in feature integration time.
\item Reorganized the project structure, creating multiple build targets for a streamlined build process, reducing build time by 25\%.
\item Presented valuable insights to the design team, enhancing designer's understanding of UI/UX traits and trends in the iOS ecosystem, resulting in a 40\% improvement in design quality and user satisfaction.
    
\end{zitemize}

%====================
% Fiverr/Upwork
%====================
\subsection{{Professional Freelancer / \href{https://www.fiverr.com/users/takausrazeem}{Fiverr}/\href{https://www.upwork.com/freelancers/~018bcc7acbf1d3e149}{Upwork} (Python|Pyrogram|Telethon|PythonTelegramBot) \hfill June 2018 - July 2021}}
\subtext{Multiple Clients \hfill Remote Work}
\begin{zitemize}
\item Successfully managed multiple freelance projects on both Fiverr and Upwork, transforming raw client requirements into profitable final products for 10+ clients, achieving a 100\% client satisfaction rate.

\item Helped FreeForex.co grow from a hundred customers to over 10,000 customers and automate the user login flow to get into the premium groups by building a login based on chat steps with the bot.

\item Developed and administered a bot for LinkChain CO, facilitating the management of organization's official group with over 20,000 members.

\item Played a crucial role in assisting numerous clients in achieving business growth and automation through Telegram bot development, contributing to a 40\% average increase in client efficiency and customer engagement.
\end{zitemize}

%====================
% WiseDigitalSolutions
%====================
\subsection{{Mobile Application Developer and Consultant \hfill March 2020 - September 2020}}
\subtext{\href{https://wisedigitalsolutions.com/}{Wise Digital Solutions} \hfill Rawalpindi, Punjab}
\begin{zitemize}
\item Examined the development of existing iOS Projects and provided consultancy on incoming projects. Also, providing estimations on cost and time for new features.    

\item Collaborated closely with the web team to maintain synchronization in development.
\end{zitemize}

%====================
% Aptech Computer Education
%====================
\subsection{{Skills Trainer / iOS/Android/C/C++/OOP \hfill November 2019 - May 2020}}
\subtext{\href{https://aptech-education.com.pk/}{Aptech Computer Education} \hfill Rawalpindi, Punjab}
\begin{zitemize}
\item Trained students for corresponding courses and polished programming skills in the mentioned areas by conducting programming tests to assess students' progress.

\item Contributed to the improvement of the curriculum.
    
% \item In fringilla purus malesuada lectus imperdiet pulvinar.
% \item Nulla eu dolor congue, mollis dui a, eleifend purus.
\end{zitemize}

%====================
% Connect Game Studio
%====================
\subsection{{iOS Developer \hfill October 2019 - March 2020}}
\subtext{\href{https://www.linkedin.com/company/connect-games-studio/}{Connect Games Studio} \hfill Gujranwala, Punjab}
\begin{zitemize}
\item Collaborated closely with the Web and Android teams to ensure synchronization between iOS Development and other platforms.

\item Coordinated with backend engineers to ensure that RESTful APIs delivered optimal performance and responsiveness.
    
\end{zitemize}

%====================
% SemangiX
%====================
\subsection{{iOS Developer / CEO \hfill September 2018 - September 2019}}
\subtext{\href{https://www.facebook.com/SemangiX/}{SemangiX} \hfill Gujranwala, Punjab}
\begin{zitemize}
\item Collaborated closely with backend engineers to optimize the (RESTful) API used by the app, resulting in a 20\% reduction in data retrieval times and a 15\% increase in overall application performance.
\item Played a pivotal role in securing a major client and took charge of managing two projects directly for both iOS and Android platforms, including planning and executing agile sprints, contributing to a 30\% increase in annual revenue.
\item Actively co-ordinated team skill development, leading to a 40\% increase in the team's proficiency in new technologies and methodologies.
\item Facilitated onboarding for new team members, reducing the time to productivity by 30\% and ensuring a smooth transition into the team.
    
\end{zitemize}

%====================
% Institute of Arts and Sciences
%====================
\subsection{{Visiting Lecturer / Visual Programming in Java\hfill January 2019 - August 2019}}
\subtext{\href{https://iasgc.edu.pk/}{Institute of Arts and Sciences} \hfill Gujranwala, Punjab}
\begin{zitemize}
\item Taught and guided 3 classes assigned by Institute management, consistently achieving a student satisfaction rate of 90\% or above.

\item Facilitated practical programming sessions, leading to an 80\% increase in students' ability to apply programming concepts to real-world scenarios.
    
\end{zitemize}

%====================
% Mobizion
%====================
\subsection{{iOS Developer Intern\hfill December 2017 - May 2018}}
\subtext{\href{https://www.mobizion.com/}{Mobizion} \hfill Daska, Punjab}
\begin{zitemize}
\item Gained proficiency in iOS Development under the guidance of experienced seniors, contributing to the successful completion of several mobile app features.

\item Efficiently executed and reported on daily tasks, consistently meeting project deadlines and quality standards.
    
\end{zitemize}

%====================
% Teacher Assistant
%====================
\subsection{{Teacher Assistant \hfill January 2016 - January 2017}}
\subtext{\href{https://www.facebook.com/uosgrw.official/}{University of Sargodha, Gujranwala Campus} \hfill Gujranwala, Punjab}
\begin{zitemize}
\item Led and supervised labs for Object-Oriented Programming and Web System \& Technologies, resulting in a 80\% increase in student participation and engagement.

\item Assisted in grading assignments and quizzes, consistently maintaining a grading speed of 30 assignments per hour.
    
\end{zitemize}

\end{document}
